Inc COVID-19 Case Forecast Eval: Results

### 2023-05-16 Code/Manuscript_figures.Rmd
removed some commented out code

  start_date <-as.Date("2020-07-28")
  stop_date <-as.Date("2022-02-22")

  df <-df %>%
    filter(sub_date >= start_date & sub_date <= cut_date) %>% #stop_date) %>%
    dplyr::select(forecast_date, model, location, target, sub_date) %>%
    distinct() %>%
    dplyr::select(-target) %>%
    distinct() %>%
    group_by(sub_date, model) %>%
    summarize(locs=n()) %>%
    ungroup() %>%
    mutate(total_sub=length(unique(sub_date))) %>%
    group_by(model) %>%
    mutate(wks_sub=length(sub_date),
           per_sub=(wks_sub/total_sub)) %>%
    ungroup() %>%
  dplyr::select(-locs, -sub_date) %>%
  distinct()

@@

#options(scipen = 999)

@@

Fig6 <-annotate_figure(
  grid.arrange(Fig6.A, Fig6.D,
               Fig6.B, Fig6.E,
               Fig6.C, Fig6.F,
             #Fig6.D, Fig6.H,
             ncol=2),
          bottom = text_grob("*U.S. counties with a population of at least 93,230 people \n", hjust=1, x=1, face = "italic", size = 10))

@@

  marg_means[[i]] <-ggemmeans(model[[i]], terms=c("phase")) %>% #, "cases_log_std[-2:2]")) %>%
    rename(phase=x,
           cases=group) %>%

>>>>

  start_date <-as.Date("2020-07-28")

  df <-df %>%
    filter(sub_date >= start_date & sub_date <= cut_date) %>% 
    dplyr::select(forecast_date, model, location, target, sub_date) %>%
    distinct() %>%
    dplyr::select(-target) %>%
    distinct() %>%
    group_by(sub_date, model) %>%
    summarize(locs=n()) %>%
    ungroup() %>%
    mutate(total_sub=length(unique(sub_date))) %>%
    group_by(model) %>%
    mutate(wks_sub=length(sub_date),
           per_sub=(wks_sub/total_sub)) %>%
    ungroup() %>%
  dplyr::select(-locs, -sub_date) %>%
  distinct()

@@

@@

Fig6 <-annotate_figure(
  grid.arrange(Fig6.A, Fig6.D,
               Fig6.B, Fig6.E,
               Fig6.C, Fig6.F,
             ncol=2),
          bottom = text_grob("*U.S. counties with a population of at least 93,230 people \n", hjust=1, x=1, face = "italic", size = 10))

@@

  marg_means[[i]] <-ggemmeans(model[[i]], terms=c("phase")) %>% 
    rename(phase=x,
           cases=group) %>%
